Survival Analysis

### 2014-04-03 presentation.Rnw
Oh shit more fixing discarded data

bfeed.poverty.all <-
  ggsurv(survfit(Surv(duration, delta) ~ poverty, data = subset(bfeed, duration > 20))) +
  ggtitle('Breast Feeding Duration by Poverty, Duration > 20 Weeks') +
  xlab('Duration in Weeks') +
  ylab('Survival') +
  geom_vline(aes(xintercept = 27),
    colour = 'red',
    linetype = 'longdash')

>>>>

bfeed.tail <- bfeed
bfeed.tail$duration <- with(bfeed.tail, ifelse(duration > 20, duration, 20))
bfeed.poverty.all <-
  ggsurv(survfit(Surv(duration, delta) ~ poverty, data = subset(bfeed.tail, duration > 20))) +
  ggtitle('Breast Feeding Duration by Poverty, Duration > 20 Weeks') +
  xlab('Duration in Weeks') +
  ylab('Survival') +
  geom_vline(aes(xintercept = 27),
    colour = 'red',
    linetype = 'longdash')
